---
title: "Reproducibility review of: Investigating the Generalizability of Segment Anything Model for Large-Scale Geospatial Segmentation"
author: "Daniel Nüst \\orcid{0000-0002-0024-5046}"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  pdf_document:
    toc: false
papersize: a4
header-includes:
  - |
    % https://tex.stackexchange.com/questions/445563/ieeetran-how-to-include-orcid-in-tex-pdf-with-pdflatex/445583 (works with pdflatex)
    \usepackage{scalerel}
    \usepackage{tikz}
    \usetikzlibrary{svg.path}
    \definecolor{orcidlogocol}{HTML}{A6CE39}
    \tikzset{
      orcidlogo/.pic={
        \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
        \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                     svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z     M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                     svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
      }
    }
    \newcommand\orcid[1]{\href{https://orcid.org/#1}{\raisebox{0.15 em}{\mbox{\scalerel*{
    \begin{tikzpicture}[yscale=-1, transform shape]
    \pic{orcidlogo};
    \end{tikzpicture}
    }{|}}}}}
    \definecolor{agileblue}{RGB}{0,77,155}
urlcolor: agileblue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r logo, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', out.width='0.3\\linewidth', fig.pos='H'}
temp <- tempfile(fileext = ".pdf")
download.file(url = "https://reproducible-agile.github.io/public/images/reproducible-AGILE-logo-square.pdf", destfile = temp)
knitr::include_graphics(temp)
```

This report is part of the reproducibility review at the AGILE conference.
For more information see [https://reproducible-agile.github.io/](https://reproducible-agile.github.io/).
This document is published on ResearchEquals TODO LINK HERE.
To cite the report use

<!-- https://researchequals.com/outputs/03981165-03b1-4b1f-9d42-32389d7d6ae1/draft -->

> TODO FULL REPORT CITATION HERE

# Reviewed paper

TODO ADD FULL CITATION

# Summary

- Result of the reproduction
- main outcome or figure

\clearpage

# Reproducibility reviewer notes

The article comprises an analysis of the performance of different machine learning models.
It provides a clear Data and Software Availability section that points to the following resources, which are the starting point for the reproduction:

> _Both datasets are open source (Werner et al., 2023; Li et al., 2021). The code and preprocessed datasets are available at the following links:_
> 
> • Code repository: <https://github.com/tum-bgd/2026-AGILE-GeoFM>
> • BBD: <https://figshare.com/s/83c2cead0d8fcc65dc6c>
> • Surface Water Dataset: <https://figshare.com/s/a359b71447c18d02b9db>

I forked the code repository to <https://github.com/reproducible-agile/2026-AGILE-GeoFM> at commit `0deeb785ac77cf4a27f2ae3f4334b6e9822b9970` to preserve the reproduction state and cloned the fork locally.
Then I followed the instructions in the README.

The commands from section **Download Checkpoints for GroundingDINO, RemoteCLIP and RemoteSAM** 

The clone operation from **Download RemoteSAM GitHub Repository** completes without error, though I'm not sure I clone it to the right location, because the README does not specify where to clone it to, and RemoteSam is not in the `.gitignore` of the project.

In section **Data** the README properly references the original datasets, but for the preprocessed/cleaned data it, the links point to private records on Figshare without a DOI.
The preprocessing is _not_ checked. The preprocessing script for _Surface Water_ is provided in the project, for _BBD_ there seems to be no script but only a minimal description of manual (?) cleaning steps.
The download, however, works, and I save the zip files in the `/data` directory and unzip them there with some manual adjustments because of different file structures, which hopefully results in the expected folder structure.
The existing files `water1k_data_filtered.csv` and `bbd1k_data_filtered.csv` are overwritten by the extraction.

While the downloads are running, I start building the Docker image as documented in **Environment** with `docker build -t python-geofm .` (because of local issues with Docker I needed to add `--network=host`) and the build runs through.

When I try to run the provided command to start the container, I get an error related to the GPU:

```bash
docker run --gpus device=1 --name geofm-container -d -it --mount type=bind,source="$(pwd)",target=/GEO python-geofm
7390c4411bab427bd66562aadfbacee806e144a131a78c575495a2f8932ccedd
docker: Error response from daemon: failed to create task for container: failed to create shim task: OCI runtime create failed: runc create failed: unable to start container process: error during container init: error running prestart hook #0: exit status 1, stdout: , stderr: Auto-detected mode as 'legacy'
nvidia-container-cli: initialization error: load library failed: libnvidia-ml.so.1: cannot open shared object file: no such file or directory: unknown

Run 'docker run --help' for more information
```

Leaving out the `--gpus` option results in the container starting, but I am not sure I can run any of the scripts because of missing GPU support.

I continue:

```bash
docker cp geofm-container:/GEOtmp/GroundingDINO ./GroundingDINO
Successfully copied 34.7MB to /home/daniel/git/reproducible-agile/reviews-2026/reports/018/2026-AGILE-GeoFM/GroundingDINO
```

In the commands for running the models, _it is unclear with parametrization is needed to conduct the same steps as in the original work_.

I try the first command with an additional `base` option, hoping that will be quicker:

```bash
root@69c678a97640:/GEO# python3 src/sam_gt_prompt.py --dataset bbd1k --model_name base
total images: 4650
The device used is cpu
/opt/conda/lib/python3.10/site-packages/huggingface_hub/file_download.py:949: FutureWarning: `resume_download` is deprecated and will be removed in version 1.0.0. Downloads always resume when possible. If you want to force a new download, use `force_download=True`.
  warnings.warn(
preprocessor_config.json: 100%|...| 466/466 [00:00<00:00, 4.21MB/s]
config.json: 6.57kB [00:00, 27.1MB/s]
model.safetensors: 100%|...| 375M/375M [00:39<00:00, 9.61MB/s]
  0%|                                                                                                                                          | 2/4650 [00:20<13:01:14, 10.08s/it]
```

It seems to pick up the CPU - good.

Aborted the computations after some time because I'd rather spend efforts on configurations/parametes matching the original work.

_Reaching out to authors now!_ Questions:

- Should CPU usage be OK?
- What are to be expected runtimes from your machines?
- What are the commands run for the analysis of the paper?
- What are the commands run to create the statistics from the paper?

--------

- technical details about reproduction
- code snippets
- summary of communication with author
- figures/screenshots
- runtime
- reproduction efforts

## Recommendations to the authors

- In the README on GitHub:
  - Include files sizes in the documentation about downloading models and data, to help users with limited bandwidth or storage to make informed decisions about what to download; use wget commands with progress information
  - Include processing times (including efforts that went into preprocessing) to manage expectations of users with limited time or computational resources, and to make preprocessing efforts more transparent
  - Provide scripted instructions for downloading and unzipping data, even from Figshare, to make sure the folder/file structure is exactly as needed
  - Add information about how the figures and statistics in the article are connected to the scripts generating them
- Provide a smaller sample dataset to evaluate your work without downloading 8+ GB of data
- Add proper metadata to the Figshare datasets and refer to them via the DOI, not use privately shared records without a DOI

```{bash some_code, eval=FALSE, size="scriptsize"}
command line code
```

```{r, echo=FALSE, eval=FALSE, results='hide'}
# create ZIP of reproduction files and upload to OSF
library("zip")
library("here")

zipfile <- here::here("PATH/agile-reproreview-YEAR-NUMBER.zip")
file.remove(zipfile)
zip::zipr(zipfile,
          here::here("2020-018/files to add to the zip, if any"))

library("osfr") # See docs at https://docs.ropensci.org/osfr/
# OSF_PAT is in .Renviron in parent directory
# We cannot use osfr to create a new component (with osfr::osf_create_component(x = osfr::osf_retrieve_node("6k5fh"), ...) because that will set the storage location to outside Europe.

# retrieve project
project <- osfr::osf_retrieve_node("OSF ID")

# upload files
osfr::osf_upload(x = project,
                 conflicts = "overwrite",
                 path = c(list.files(here::here("PATH"),
                                     pattern = "agile-reproreview-.*(pdf$|Rmd$|zip$)",
                                     full.names = TRUE),
                          "COPYRIGHT"
                          )
                 )
```